---
title: "Simple document"
output: github_document
---

# Problem 1

```{r}
data("penguins", package = "palmerpenguins")
```
**Description**: 

*   1. Important variables
    * The species of penguins includes: `r paste(unique(penguins$species), collapse = ", ")`
    * The islands of oringin includes: `r paste(unique(penguins$island), collapse = ", ")`
    * The range of their bill length in mm are [`r  range(penguins$bill_length_mm, na.rm = TRUE)`]
    * The range of their bill depth in mm are [`r  range(penguins$bill_depth_mm, na.rm = TRUE)`]
    * The range of their flipper length in mm are [`r  range(penguins$flipper_length_mm, na.rm = TRUE)`]
    * The range of their body mass in g are [`r  range(penguins$body_mass_g, na.rm = TRUE)`]
    * All data are from year of `r paste(unique(penguins$year), collapse = ", ")`

*   2. Size of dataset
    * This dataset includes `r nrow(penguins)` rows, and `r ncol(penguins)` columns
    
*   3. Mean flipper length
    * The mean flipper length is `r mean(penguins$flipper_length_mm)`
    

```{r}

```


```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.