---
title: "Simple document"
output: github_document
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
```

# Problem 1

## Part 1
```{r}
data("penguins", package = "palmerpenguins")
```
**Description**: 

*   1. Important variables
    * The species of penguins includes: `r paste(unique(penguins$species), collapse = ", ")`
    * The islands of oringin includes: `r paste(unique(penguins$island), collapse = ", ")`
    * The range of their bill length in mm are [`r  range(penguins$bill_length_mm, na.rm = TRUE)`]
    * The range of their bill depth in mm are [`r  range(penguins$bill_depth_mm, na.rm = TRUE)`]
    * The range of their flipper length in mm are [`r  range(penguins$flipper_length_mm, na.rm = TRUE)`]
    * The range of their body mass in g are [`r  range(penguins$body_mass_g, na.rm = TRUE)`]
    * All data are from year of `r paste(unique(penguins$year), collapse = ", ")`

*   2. Size of dataset
    * This dataset includes `r nrow(penguins)` rows, and `r ncol(penguins)` columns
    
*   3. Mean flipper length
    * The mean flipper length is `r mean(penguins$flipper_length_mm)`
    
## Part 2
```{r}

scatterplot <- ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point(na.rm = TRUE) +
  labs(
    title = "Scatterplot of Flipper Length vs Bill Length",
    x = "Bill Length (mm)",
    y = "Flipper Length (mm)"
  ) +
  theme_classic()

ggsave(filename = "scatterplot_flipper_vs_bill.png", plot = scatterplot, width = 10, height = 10, dpi = 300)

print(scatterplot)
```

# Problem 2

Start with generate random vectors and combine them into a data frame
```{r}

set.seed(123)

# Set random vectors
random_sample = rnorm(10)
logical_vector = random_sample > 0
char_vector = sample(c("我", "爱", "你", "中", "国"), size = 10, replace = TRUE)
factor_vector = factor(sample(c("Level1", "Level2", "Level3"), size = 10, replace = TRUE))

# Create a data frame with vectors
df <- data.frame(
  random_sample = random_sample,
  logical_vector = logical_vector,
  char_vector = char_vector,
  factor_vector = factor_vector
)

```

Then get the mean of these random vectors with 'pull()' function.
```{r}
mean_rs = mean(pull(df, random_sample))
mean_lv = mean(pull(df, logical_vector))
mean_cv = mean(pull(df, char_vector))
mean_fv = mean(pull(df, factor_vector))
```

Of 4 random vectors, we can get the mean of random_sample and logical_vector, we cannot get the mean of character_vector and factor_vector. 
Should convert them into a different type. 

```{r}
as.numeric(pull(df, logical_vector))
as.numeric(pull(df, char_vector))
as.numeric(pull(df, factor_vector))
```

The 'True' and 'False' value in logical_vector is converted to 1 and 0, allowing the calculation of mean; the value in char_vector are still returning N/A, indicating that one still cannot get the mean; the value in factor_vector are converted to numeric value, allowing the calculation of mean.
# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.